Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
update table II entries

\begin{table}
\begin{center}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
ei (linear)  & 54 (20)       & 62 (6)  & 66 (11)     \\
ei (RBF)     & 47 (16)       & 56 (7)  & 63 (6)    \\
li (linear)  & 60  (9)       & 70 (8)  & 75 (5)   \\
li (RBF)     & 68 (10)       & 73 (8)  & 78 (6)   \\
\end{tabular}
\caption{Accuracies for the best settings}
\end{center}
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
early (linear)  & 54 (20)       & 62 (6)  & 66 (11)     \\
early (RBF)     & 47 (16)       & 56 (7)  & 63 (6)    \\
late (linear)  & 60  (9)       & 70 (8)  & 75 (5)   \\
late (RBF)     & 68 (10)       & 73 (8)  & 78 (6)   \\
\end{tabular}
\caption{Accuracies for the best settings}
\end{center}
\end{table}
